Neighbor-Based Decentralized Training Strategies for Multi-Agent Reinforcement Learning

### 2024-10-12 paper-2024-sac-marl-neighbouring-strategies.tex
add performance comparison and scalability

>>>>

\paragraph{Performance comparison}
The results -- \Cref{fig:results} -- shows that employing a centralized training (i.e., CTDE) approach allows the model to converge 
 more rapidly -- in terms of episodes -- to a higher reward compared to a fully decentralized approach (i.e., DTDE). 
%
This difference becomes even more evident when considering the Mean Episode Length metric, where CTDE not only converges 
 faster but also solves the task using shorter episodes than DTDE.

Additionally, we implemented another state-of-the-art algorithm, namely MAPPO, as a baseline for comparison. 
%
However, MAPPO performed worse than both CTDE and DTDE across both metrics -- yielding lower results and exhibiting less stability, 
 as reflected in its higher standard deviation.

Regarding the proposed neighbor-based approaches, it can be observed that both \emph{experience sharing} and 
 \emph{NN averaging} enhance the performance of DTDE, achieving results comparable to CTDE while also increasing 
 learning stability. 
% 
On the other hand, \emph{NN consensus} maintains performance levels similar to DTDE, which may be attributed to the 
 simplicity of the implemented consensus policy. 
%
Nevertheless, it remains more stable and achieves better performance than MAPPO.

\paragraph{Scalability}
To evaluate the scalability of the learned policies, we conducted several experiments by increasing the number 
 of agents -- specifically to 8, 16, and 32 -- and measuring the time required to complete the task 
 (i.e., mean episode length).

The results -- \Cref{fig:time-eval} -- show that as the number of agents increases, DTDE exhibits both a higher mean time 
 to solve the task and greater instability. 
%
In contrast, CTDE, NN averaging, and experience sharing maintain strong performance. 
%
Similar to the training phase, NN consensus does not achieve the same results as the other two neighbor-based 
 approaches but remains on par with DTDE in terms of performance.

\paragraph{Communication overhead}
